Data for ms. 1

### 2017-04-12 ms1/ms1.Rmd
updates

  claims_by_age_group = dat$usage %>%
    mutate(age_group=age_group_f(age)) %>%
    group_by(age_group) %>%
    summarize(n_claims=sum(n_claims), n_bene=n()) %>%
    mutate(cpkp=n_claims*1000/n_bene) %>%
    select(age_group, n_bene, cpkp)

@@

  list(totals=totals,
       claims_by_class=claims_by_class,
       top_abx=top_abx,
       claims_by_sex=claims_by_sex,
       claims_by_age=claims_by_age,
       claims_by_age_group=claims_by_age_group,
       claims_by_region=claims_by_region,
       chars_by_consumption=chars_by_consumption,
       condition_model=condition_model) %>%
    lapply(function(x) mutate(x, year=year))
}

@@

claims_by_age_group = data_by_field('claims_by_age_group') %>%
  mutate(cpkp=round(cpkp)) %>%
  select(age_group, year, cpkp) %>%
  spread(year, cpkp) %T>%
  write_tsv('tables/supptable1_age_group.tsv') %>%
  kable

@@

condition_model = data_by_field('condition_model') %>%
  left_join(condition_names, by='condition') %>%
  filter(year==2011, term != '(Intercept)') %>%
  mutate(estimate=round(estimate, digits=3)) %>%
  select(condition=condition_name, term, estimate) %>%
  spread(term, estimate) %>%
  arrange(desc(has_conditionTRUE)) %T>%
  write_tsv('tables/table3.tsv') %>%
  kable
```

@@

>>>>

  chars_by_age_group = dat$usage %>%
    mutate(age_group=age_group_f(age)) %>%
    group_by(age_group) %>%
    summarize(mean_n_claims=mean(n_claims), mean_n_cc=mean(n_cc)) %>%
    mutate(cpkp=mean_n_claims*1000) %>%
    select(age_group, cpkp, mean_n_cc)

@@

  list(totals=totals,
       claims_by_class=claims_by_class,
       top_abx=top_abx,
       claims_by_sex=claims_by_sex,
       claims_by_age=claims_by_age,
       chars_by_age_group=chars_by_age_group,
       claims_by_region=claims_by_region,
       chars_by_consumption=chars_by_consumption,
       condition_model=condition_model) %>%
    lapply(function(x) mutate(x, year=year))
}

@@

chars_by_age_group = data_by_field('claims_by_age_group') %>%
  mutate(cpkp=round(cpkp), mean_n_cc=round(mean_n_cc, digits=2)) %>%
  select(age_group, year, cpkp, mean_n_cc) %>%
  gather('variable', 'value', cpkp, mean_n_cc) %>%
  mutate(variable=interaction(year, variable)) %>%
  select(-year) %>%
  spread(variable, value) %T>%
  write_tsv('tables/supptable1_age_group.tsv') %>%
  kable

@@

condition_model_all_years = data_by_field('condition_model') %>%
  left_join(condition_names, by='condition') %>%
  filter(term != '(Intercept)') %>%
  mutate(estimate=round(estimate, digits=3)) %>%
  select(year, condition=condition_name, term, estimate) %T>%
  write_tsv('tables/supptable4_singlecondition.tsv')

condition_model = condition_model_all_years %>%
  filter(year==2011) %>% select(-year) %>%
  spread(term, estimate) %>%
  arrange(desc(has_conditionTRUE)) %T>%
  write_tsv('tables/table3.tsv') %>%
  kable
```

@@

`r chars_by_age_group`
